EP1162 Preliminary Analysis

### 2020-03-10 analysis/prelimAnalysis.Rmd
A few adjustments to analysis.

  # Plotting
  ggplot()+
  aes(x=Period,y=PBAI.mean,fill=Trt.Unit,color=Trt.Unit,group=Trt.Unit)+
  geom_point(size=3)+
  geom_line()+
  geom_errorbar(aes(ymin=PBAI.mean-PBAI.se,ymax=PBAI.mean+PBAI.se),width=0.1)+
  xlab("Period")+
  ylab("Mean basal area per plot (m2/ha)")

>>>>

  # Plotting
  ggplot()+
  aes(x=Period,y=PBAI.mean,fill=Trt.Unit,color=Trt.Unit,group=Trt.Unit)+
  geom_point(size=3)+
  geom_line()+
  geom_errorbar(aes(ymin=PBAI.mean-PBAI.se,ymax=PBAI.mean+PBAI.se),width=0.1)+
  xlab("Period")+
  ylab("Mean BAI per plot (m2/ha/period)")
